Astr 513: Final Project

### 2016-05-07 Final_Project/ms.tex
Added code that make corner plots. Added betoule figures for lcdm.

\begin{figure}
  \centering
  \includegraphics[width=0.6\linewidth]{figures/betoule_wcdm_noprior_corner.eps}
  \caption{Posterior distributions of the cosmological parameters in the
    analysis of the \citet{Betoule2014} data without including the
    \Planck priors. Contours denote the
    68\% and 95\% confidence projected areas; dashed lines in
    the 1D histograms refer to the 68\% confidence intervals.}
  \label{fig:betoule_wcdm_noprior_corner}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.6\linewidth]{figures/betoule_wcdm_withprior_corner.eps}
  \caption{Posterior distributions of the cosmological parameters in the
    analysis of the \citet{Betoule2014} data including the
    \Planck priors. Contours denote the
    68\% and 95\% confidence projected areas; dashed lines in
    the 1D histograms refer to the 68\% confidence intervals.}
  \label{fig:betoule_wcdm_withprior_corner}
\end{figure}

@@

\appendix
\section{Posterior Distribution Functions Without \Planck Priors}
\TM{Since there are potentially a bunch of corner plots, we could jam a bunch of
  them here as well as perhaps the discussion of what happens when we remove
  the priros. Let me know your thoughts.}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.6\linewidth]{figures/betoule_wcdm_noprior_corner.eps}
  \caption{Posterior distributions of the cosmological parameters in the
    analysis of the \citet{betoule2014} data without including the
    \Planck priors for a wCDM model. Contours denote the
    68\% and 95\% confidence projected areas; dashed lines in
    the 1D histograms refer to the 68\% confidence intervals.}
  \label{fig:betoule_wcdm_noprior_corner}
\end{figure}
%
\begin{figure}
  \centering
  \includegraphics[width=0.6\linewidth]{figures/betoule_wcdm_withprior_corner.eps}
  \caption{Posterior distributions of the cosmological parameters in the
    analysis of the \citet{betoule2014} data including the
    \Planck priors for a wCDM model. Contours denote the
    68\% and 95\% confidence projected areas; dashed lines in
    the 1D histograms refer to the 68\% confidence intervals.}
  \label{fig:betoule_wcdm_withprior_corner}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.6\linewidth]{figures/betoule_lcdm_noprior_corner.eps}
  \caption{Posterior distributions of the cosmological parameters in the
    analysis of the \citet{betoule2014} data without including the
    \Planck priors for a $\Lambda$CDM model. Contours denote the
    68\% and 95\% confidence projected areas; dashed lines in
    the 1D histograms refer to the 68\% confidence intervals.}
  \label{fig:betoule_lcdm_noprior_corner}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.6\linewidth]{figures/betoule_lcdm_withprior_corner.eps}
  \caption{Posterior distributions of the cosmological parameters in the
    analysis of the \citet{betoule2014} data including the
    \Planck priors for a $\Lambda$CDM model. Contours denote the
    68\% and 95\% confidence projected areas; dashed lines in
    the 1D histograms refer to the 68\% confidence intervals.}
  \label{fig:betoule_lcdm_withprior_corner}
\end{figure}

@@
